### 2024-09-17 base-rates.qmd
20240917 - updates

The function can also create a nomogram plot using the [sensitivity](#sec-sensitivity) (SN) and [false positive rate](#sec-falsePositiveRate) of the test.
Here is a nomogram plot from [Example 1](#sec-nateSilverExample1) from @Silver2012 (where [specificity](#sec-specificity) equals 1 minus the [false positive rate](#sec-falsePositiveRate)):

@@

Here is a nomogram plot from [Example 2](#sec-nateSilverExample2) from @Silver2012 (where [specificity](#sec-specificity) equals 1 minus the [false positive rate](#sec-falsePositiveRate)):

@@

Here is a nomogram plot from [Example 3A](#sec-nateSilverExample3A) from @Silver2012 (where [specificity](#sec-specificity) equals 1 minus the [false positive rate](#sec-falsePositiveRate)):

@@

Here is a nomogram plot from [Example 3B](#sec-nateSilverExample3B) from @Silver2012 (where [specificity](#sec-specificity) equals 1 minus the [false positive rate](#sec-falsePositiveRate)):

>>>>

The function can also create a nomogram plot using the [sensitivity](#sec-sensitivity) (SN) and [false positive rate](#sec-falsePositiveRate) of the test.
Here is a nomogram plot from [Example 1](#sec-nateSilverExample1) from @Silver2012:

@@

Here is a nomogram plot from [Example 2](#sec-nateSilverExample2) from @Silver2012:

@@

Here is a nomogram plot from [Example 3A](#sec-nateSilverExample3A) from @Silver2012:

@@

Here is a nomogram plot from [Example 3B](#sec-nateSilverExample3B) from @Silver2012:
